On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-12 Manuscript/manuscript.tex
reorged table 2

\jy{Add the results without 2022 to this table.}
\of{Does it make sense to order the table how I did, and block by dataset or
should I block by model?}
\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to all the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c}
      \toprule
      Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
      \midrule
      With 2022 Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
      With 2022 Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
      With 2022 Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \midrule
      Without 2022 Venue Effect Only & $-1862.2$ &   & 0.048 & $-1.857$ & 0.152\\
      Without 2022 Heat Effect Only & $-1910.9$ & 0.069 &  & $-1.877$ & 0.136\\
      Without 2022 Venue and Heat Effect & $-1912.9$ & 0.058 & 0.033 & $-1.880$ & 0.136\\
      \bottomrule
  \end{tabular}
\end{table}

>>>>

\jy{Add the results without 2022 to this table.}
\of{Does it make sense to order the table how I did, and block by dataset or
should I block by model?}
\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c c}
    \toprule
    Data set & Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
    \midrule
    Excluding 2022 &
      Venue Effect Only & $-1862.2$ &   & 0.048 & $-1.857$ & 0.152\\
     & Heat Effect Only & $-1910.9$ & 0.069 &  & $-1.877$ & 0.136\\
     & Venue and Heat Effect & $-1912.9$ & 0.058 & 0.033 & $-1.880$ & 0.136\\[1ex]
    Including 2022 &
    Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
    & Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
    & Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
    \bottomrule
  \end{tabular}
\end{table}
